### 2016-08-15 Chapters/Ch04-PaperSummary.tex
Save work on CC chapter

\refstepcounter{dummy}
\addcontentsline{toc}{section}{\tocEntry{Continuum solvation in the relativistic regime}}
\section*{Paper I. Continuum solvation in the relativistic regime}

@@

\refstepcounter{dummy}
\addcontentsline{toc}{section}{\tocEntry{The wavelet Galerkin boundary element method for PCM}}
\section*{Paper II. The wavelet Galerkin boundary element method for PCM}

@@

\refstepcounter{dummy}
\addcontentsline{toc}{section}{\tocEntry{Continuum modelling of non homogeneous environments}}
\section*{Paper III: Continuum modelling of non homogeneous environments}

@@

\refstepcounter{dummy}
\addcontentsline{toc}{section}{\tocEntry{Relativistic calculation of EPR and pNMR parameters in solution}}
\section*{Paper IV: Relativistic calculation of EPR and pNMR parameters in solution}

\refstepcounter{dummy}
\addcontentsline{toc}{section}{\tocEntry{Open-ended self-consistent field response theory in solution}}
\section*{Paper V: Open-ended self-consistent field response theory in solution}

>>>>

\refstepcounter{dummy}
\addcontentsline{toc}{section}{Continuum solvation in the relativistic regime}
\section*{Paper I. Continuum solvation in the relativistic regime}

@@

\refstepcounter{dummy}
\addcontentsline{toc}{section}{The wavelet Galerkin boundary element method for PCM}
\section*{Paper II. The wavelet Galerkin boundary element method for PCM}

@@

\refstepcounter{dummy}
\addcontentsline{toc}{section}{Non homogeneous environments}
\section*{Paper III: Non homogeneous environments}

@@

\refstepcounter{dummy}
\addcontentsline{toc}{section}{Relativistic calculation of EPR and pNMR parameters in solution}
\section*{Paper IV: Relativistic calculation of EPR and pNMR parameters in solution}

\refstepcounter{dummy}
\addcontentsline{toc}{section}{Open-ended self-consistent field response theory in solution}
\section*{Paper V: Open-ended self-consistent field response theory in solution}
